### 2017-07-14 architecture.tex
Editing impl

% Why do we have them / inital role
As more datasets with varying degrees of sensitivity are added to the \NAME platform it becomes a matter
of necessity to distribute key administrative privileges from the system administrator roles to the curators
of the data-set. Stewards play a leadership role in evaluating the disclosure risks associated with a
dataset and codifying the security protocols protecting the safe-collection.

% access
Analysts can list all available safe-collections and request access to ones that they require.
Stewards evaluate these requests and approve access for a duration. Approvals are implemented as an additional
policy added to the list of s3 bucket policies for the safe-collection. \NAME ensures that the policy
being added is consistent with the meta-policy for the safe-collection, for example, expiration for the policy
must be within the duration specified in the \texttt{MaxApprovalDur}.

% export
On export controlled safe-collections, results generated by analysis tasks on \NAME are not visible to the
analysts until approved by a Steward. This is implemented by having workers write all results to the
parent safe-collections output directory and thus inheriting the same security privileges of the parent.
On \NAME stewards have complete visibility over the set of inputs, and operations made by the analysts
in order to generate their results. It is also possible to trace the provenance of the results from an
analysis pipeline since all analysis tasks are logged.
Stewards export the results by transferring the results out of the safe-collection and onto a public
safe-collection from which analysts can view results. It is important to note that even public
safe-collections have server side encryption and are only accessible to authenticated users via temporary
signed URLs.

@@

We extend our AWS-based \NAME services by leveraging additional
services and guarantees provided by AWS. 
Safe-collection policies are expressed on \NAMENS's S3-hosted data
%The data-store is implemented over S3 object store, and the
using Identity and Access Management(IAM) policies and S3 bucket policies.
A safe-collection is described in cloudformation, a JSON-based software defined infrastructure model for AWS.
This allows safe-collection descriptions to be verifiable, reproducible, and shareable.

We define a meta-policy model via which administrators may define
the set of policies permissible on a safe-collection. Each safe-collection is associated with a steward
(or group of stewards) who may manage safe-collection policies. To simplify use, the meta policy schema 
is translated to a web-based form that can be completed by users during creation of a safe-collection. 
The completed form is stored as a set of special tags on the collection's data storage. The schema is enforced
by the various services that interact with the safe-collection. The schema and the generated form are shown in
\figurename~\ref{fig:schema}

@@

% implementation of access control
Access control on safe-collections for private datasets are managed by stewards. Access privileges to
safe-collections are granted, extended, and revoked via S3 bucket policies. At the time of creation all
privileges over bucket policies are granted to the steward and revoked for all other entities. This
guarantees that only the stewards can grant privileges on a safe-collection. Access is granted by stewards
by adding a new bucket policy conditional on an expiration deadline. These policies may be revoked or
extended by updating the expiration deadline, thus offering fine-grained control to stewards on managing
access.

% implementation details
Upon creation of a safe-collection a single steward group implemented as an IAM role, is added to the
access policies of the safe-collection. This steward role is the sole entity on the platform capable of
updating polices attached to the safe-collection.
Multiple users could be associated with a steward role and is recommended, so that requests can be served quicker.
Once user identities are established by authenticating with an external identity provider,
\NAME allows users to ``assume'' a privileged IAM role that they have been attached to.
By assuming the steward role, a user temporarily gains the privileges to carry out operations such
as updating access policies and exporting data from a safe-collection.
Once created the steward's responsibilities are two-fold: arbitrate access requests to the safe-collection and
handle export requests for results generated from safe-collections.

>>>>

% Why do we have them / inital role
As that number of datasets managed by \NAME increase it is crucial that administrative
tasks are distributed to individual collection administrators. This separates
concerns from those that operate \NAME and those that manage the data stored in \NAMENS.
Stewards play a leadership role in evaluating the disclosure risks associated with a
dataset and codifying the security protocols protecting the safe-collection.

Stewards are responsible for activities such as approving access to a collection, reviewing
export requests, and managing policies on the collection. Users (e.g., analysts) can discover
and then obtain access to safe collections by listing available safe collections and requesting
access to individual collections. 
Stewards are presented with a list of user requests and must explicitly approve access
for a specific duration. Throughout the duration of a user's access to a collection
stewards may review their actions and revoke access at any time. When users attempt
to export data from an export controlled safe-collection, the data is not immediately
accessible to the user. Rather, the exported data is collected and stored privately
such that a steward can approve the export request. Finally, approved data exports
are turned over to the user.

@@

The \NAME service is built upon a set of reliable and secure
AWS services. We extend this architecture to support safe collections
by building upon additional AWS capabilities and services.

Safe collection policies are expressed on \NAMENS's managed
data via AWS Identity and Access Management (IAM) policies 
and S3 bucket policies.
A safe collection is described in CloudFormation templates, where 
CloudFormation provides a reproducible method for instantiating infrastructure
based on a standard JSON description. For example, it defines
the S3 bucket to be used as well as the secure connections
to the rest of the \NAME system.
\kyle{I dont understand exactly how CloudFormation describes the collection? Is
what I wrote correct?}
%This allows safe-collection descriptions to be verifiable, reproducible, and shareable.

To enable the definition and management of safe collection policies we 
rely on a meta-policy model. The meta-policy model enables specification
of the policies described above. Each safe collection is associated with a steward
(or group of stewards) who may manage the collection's policies. To simplify use, the meta-policy schema 
is translated to a web-based form that can be completed by users during creation of a safe collection. 
The defined policies (from the form or otherwise) is stored as a set of secure tags 
on the collection's data storage bucket. The schema is enforced
by the various services that interact with the safe collection. The schema and the generated form are shown in
\figurename~\ref{fig:schema}

@@

Upon creation of a safe collection a single steward group (implemented as an IAM role) is added to the
access policies of the safe collection. This steward role is the sole entity on the platform capable of
updating policies attached to the safe collection.
Multiple users can be associated with the steward role---this is often recommended such 
that requests can be served quickly. 
Having established one's identity (via the \NAME authentication workflow) users 
may ``assume'' a privileged IAM role for which they are permitted. 
When assuming the steward role, a user temporarily gains the privileges to carry out operations such
as updating access policies and approving the export of data from a safe collection.

% implementation of access control
Access control on safe collections are managed by stewards. Access privileges for specific users
are granted, extended, and revoked via S3 bucket policies. At the time of creation all
privileges over bucket policies are granted to the steward and revoked for all other entities. This
guarantees that only the stewards can grant privileges on a safe collection. Access to other users 
is granted by stewards by adding a new bucket policy conditional on an expiration deadline. These policies may be revoked or
extended by updating the expiration deadline, thus offering fine-grained control to stewards for managing
access.

Data derived from safe collections (e.g., results from tasks that consumed data from that collection)
are stored in the same safe collection, thus inheriting the same policies as the safe collection itself.
As a result, only stewards can view the derived data and determine if it is safe to 
export the data
Stewards have complete visibility over all data that was used as input to an analysis as
well as the operations (analysis steps) made by the analysts to derive their results.
It is therefore possible to trace the entire provenance of the derived data from an
analysis pipeline since all analysis tasks are logged.
If an export request is approved, data is copied from the host collection to a public safe collection. 
It is important to note that even public safe collections have server side encryption and 
are only accessible to authenticated users via temporary signed URLs. 
As derived data are stored within the parent's safe collection, users can continue 
to perform analysis operations on results without oversight,
and only request export of data that must leave the safe collection (e.g., the
final results of a deep analysis pipeline).

Export approvals are implemented as a policy associated with the collection's bucket. 
\NAME ensures that the policy added is consistent with the meta-policy for the safe collection, 
for example, ensuring that expiration for the policy
is within the duration specified on the safe collection.

%On export controlled safe-collections, results generated by analysis tasks on \NAME are not visible to the
%analysts until approved by a Steward. This is implemented by having workers write all results to the
%parent safe-collections output directory and thus inheriting the same security privileges of the parent.
